|

### 2019-09-03 article/article.Rmd
Fix some small coding errors.

The first intervention was carried out from August 2017 to February 2018 using the Android version of TDP. The randomization was conduct at the municipal level. We randomly selected `r as.numeric(table(impEvalph1$treatOriginal)[1])` municipalities to the control group and included `r as.numeric(table(impEvalph1$treatOriginal)[2])` in the treatment group. Our control condition consists in removing all information about school construction from the TDP app in the chosen municipalities, so that citizens were unable to report constructions in the control municipalities.

@@

We also conducted two manipulation checks and analysed the number of TDP app downloads by municipality and over time. Figure \ref{fig:manipulation1} displays the results and indicates that the treatment has good territorial variability. There are `r length(unique(ga$municipality[ga$phase1==1]))` downloads in the `r length(unique(impEvalph1$municipality[impEvalph1$treatOriginal==1]))` municipalities in the treatment condition. Downloads peak during the Facebook TDP campaign, launched in October 2017, then diminish in the following months.

@@

The second intervention is similar to intervention 1 in all but three characteristics. First, the TDP app was available for both Android and iOS devices. Second, we randomised the intervention at the school level, with `r as.numeric(table(impEvalph2$treatApp)[1])` control and `r as.numeric(table(impEvalph2$treatApp)[2])` treatment units. We used blocked randomisation stratified by Brazilian states, school construction status (under construction, stopped, unfinished) and whether the municipality spent more on school construction that the distribution median. Finally, the intervention period lasted from August 2018 to February 2019.

Balance tests and manipulation checks were also successful for intervention 2. In total, `r sum(gaaux$Downloads == 'Downloads')` municipalities downloaded the app. There is one download peak in August 2018, right after intervention 2 starts, and a second spike around December. The number of downloads is considerably smaller in this second intervention when compared to intervention 1 as there was no associated social media campaign in that period.

@@

Table \ref{tab:results2} shows the results of the second intervention. The treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo. This raises further questions about the effect of the TDP app on school completion. Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 1.57 percent. However, the coefficient only reaches statistical significance when we employ inverse probability weights with block randomisation and one-to-one nearest neighbourhood matching.

@@

We also note that effect sizes are small in all estimations and coefficients flip signs in all but one of our six dependent variables. This provides further evidence for the null results: not only the app would have a low impact even if the treatment were significant, but the results could go against what the bottom-up accountability theory predicts. At least in the school construction outcomes we investigate here, we find little evidence that grassroots monitoring works. This inconsistent directions for the effects reassure us that the null is not only a matter of statistical power.

@@

In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery in the case of school constructions in Brazil. Nevertheless, the null findings are informative to researchers and policy-makers. The most important recommendation derived from this study is that interventions targeting elite groups, such as lobbyists or civil servants, may render better policy outcomes than those focused at the grassroots levels. Another core lesson is that although digital interventions are promising means to deliver information, perhaps they do not have the same impact as personal, face-to-face communication. Since many developing countries share Brazil's issues with education provision, the shortcomings we describe here serve as warnings for future interventions.

>>>>

The first intervention was carried out from August 2017 to February 2018 using the Android version of TDP. The randomization was conduct at the municipal level. We randomly selected `r as.numeric(table(impact_evaluation_phase1$treat)[1])` municipalities to the control group and included `r as.numeric(table(impact_evaluation_phase1$treat)[2])` in the treatment group. Our control condition consists in removing all information about school construction from the TDP app in the chosen municipalities, so that citizens were unable to report constructions in the control municipalities.

@@

We also conducted two manipulation checks and analysed the number of TDP app downloads by municipality and over time. Figure \ref{fig:manipulation1} displays the results and indicates that the treatment has good territorial variability. There are `r length(unique(ga$municipality[ga$phase1==1]))` downloads in the `r length(unique(impact_evaluation_phase1$municipality[impact_evaluation_phase1$treat=='Treatment']))` municipalities in the treatment condition. Downloads peak during the Facebook TDP campaign, launched in October 2017, then diminish in the following months.

@@

The second intervention is similar to intervention 1 in all but three characteristics. First, the TDP app was available for both Android and iOS devices. Second, we randomised the intervention at the school level, with `r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and `r as.numeric(table(impact_evaluation_phase2$treat)[2])` treatment units. We used blocked randomisation stratified by Brazilian states, school construction status (under construction, stopped, unfinished) and whether the municipality spent more on school construction that the distribution median. Finally, the intervention period lasted from August 2018 to February 2019.

Balance tests and manipulation checks were also successful for intervention 2. In total, `r sum(ga$Downloads[ga$phase2 == 1] == 'Downloads')` municipalities downloaded the app. There is one download peak in August 2018, right after intervention 2 starts, and a second spike around December. The number of downloads is considerably smaller in this second intervention when compared to intervention 1 as there was no associated social media campaign in that period.

@@

Table \ref{tab:results2} shows the results of the second intervention. The treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo. This raises further questions about the effect of the TDP app on school completion. Note that the effect signs are also inconsistent with improving the outcomes, what demonstrates that our results are not likely to result from low statistical power imposed by reduced control group requirement.

@@

We also note that effect sizes are small in all estimations and coefficients flip signs in all but one of our six dependent variables. This provides further evidence for the null results: not only the app would have a low impact even if the treatment were significant, but the results could go against what the bottom-up accountability theory predicts. At least in the school construction outcomes we investigate here, we find little evidence that grassroots monitoring works in the context of school constructions in Brazil.

@@

In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery in the case of school constructions in Brazil. Nevertheless, the null findings are informative to researchers and policy-makers. The most important recommendation derived from this study is that interventions targeting elite groups, such as lobbyists or civil servants, might render better policy outcomes than those focused at the grassroots levels. Another core lesson is that although digital interventions are promising means to deliver information, perhaps they do not have the same impact as personal, face-to-face communication. Since many developing countries share Brazil's issues with education provision, the shortcomings we describe here serve as warnings for future interventions.
